\textsf{Are large language models superhuman chemists?}

### 2024-10-25 src/tex/appendix.tex
fix latex syntax
feat: skillset distribution plot

In addition, as shown in \Cref{tab:chembench_corpus_cognitive} the \chembench corpus can be divided considering the different skills needed to solve the questions.

>>>>

In addition, as shown in \Cref{tab:cb_skillset} the \chembench corpus can be divided considering the different skills needed to solve the questions. The plot shows an even distribution of the required skills in the \chembench corpus. \Cref{tab:cb_skillset} shows an example question for each skill category.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/CB_SKILL_FIG_V1.pdf}
    \caption{\textbf{Composition of the required skills considered in the \ChemBench corpus.} The circular plot shows the distribution of required skills in the \chembench corpus.}
    \label{fig:cb_skillset}
\end{figure}
